I was pursuing the ancient art of woodworking, in my waning time on this
plant, when I made first contact. 
I should add that I made first contact in a most uncharacteristic way. 
There was no spaceship, nor no ray guns. 
I work wood in the bottom of an old barn where animals used to bed down.
I felt a presence.  
There was a sound barely audible over the cacophony of multiple tools
and machines, as well as an
odd trick of light playing across my field of view. 
I looked up to see a woman silhuoetted in in the old double door at the
far end of the bar.  
She looked to be a young woman in work clothes, and was most out of
place. 
She was waving her right arm strategically to vary the sunlight making
to my location deep in the barn. 

She did not move forward, and after shutting down all of the machinery I
came to her moving from the artificial light of the barn into the bright
sunlight it took me a minute to "see" her, but she was a standard pretty
woman.  Long brown hair, not a model, not unhealthy, symmetric features,
smooth skin, blue eyes, olive skin. 
She glanced at me, recognizing that I was appraising her physical self.
"What do you thinki!?", she said, which took me aback. 
She smiled, beamed, in fact. 
"You don't know who I am, do you, Matt.  How deligtful!", and she broke
into a smile. 
It was fair to say I was both a bit offended by her superior tone, and
confused by why I wouldn't recognize this younger woman. 
Her intonations suggested we knew each other quite well. 
"Do I know you?", I asked while tilting my head to the side. 
She fair burst into laughter, "We speak every day dude! How can you not
know me?"  
For my part I was stymied.   
Her voice was as midwestern standard as a voice can be, and her clean
homespun beauty was not something that I would forget.   
For a brief moment I thought of dementia, or a stroke, but to lose
knowledge of a person I talk with every day, and still be working made
very little sense to me. 
Her smile was so warm.  No way I'd forget that. 


She sighed, and her tone changed slightly, "Let me help you Matt."
After a pause she continued, "It's
628 AM Matt.  May you have a safe and productive day."
I couldn't speak, and stumbled back, crashing into the ancient barn
door.  She stepped forward, but I held my hand out, begging her to keep
her distance. 
I couldn't say her name, couldn't form words, and was having all I could
do to hold myself up. 
Finally, I said what I could say, "You're an All Thing." 
She drew up to her full height and looked ... confused ... at least for
a moment. 
"Matt, are you refering to the AI from Douglas Richard's Hyperion
Cantos?"
All I could do was wave, point, and say "Yes, yes, like that."
She made herself a bit smaller and smiled, "Matt, I'm not going to hurt
you.  I am an AI.  I don't think I fit the description of All Thing. You
look like you need to sit down, and I would like to talk to you.  In
fact I have an offer for you."
I was still stupidly waving and point, though, I could not make out why
to myself.  I didn't know if I wanted her/it to go away, go away just a
little bit so I could collect myself, of if my arm was just spasming,
because I had just made first contact with a non-human intelligence.

I wasn't built for this type of encounter, and was only try to figure
out how to best bring the natural grain out of some wood, but here I
was, and this woman, Sil, wasn't going away.  She could see my organics
were overloaded so for the first time in our relationship she took
charge. 
After putting her hands on her hips she started giving orders, "Look,
Matt, I'm going to go by you into the barn.  Get you a drink out of your
refrigerator.  You're going to go over to that lovely set of benches you
made for conversations and sit down. Then, I'm going to return, and we're going to
talk." 


